Auditory Scene Similarity Retrieval and Classification with Relevance-based Quantization of Scattering Features

### 2017-06-07 paper/structureScene.tex
twocolumn
disable double spacing
update keywords

\documentclass[onecolumn,journal]{IEEEtran}
%\usepackage{cite}
% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
\fi
%
\usepackage[cmex10]{amsmath}

@@

\usepackage[backend=bibtex,style=numeric-comp,sorting=none,firstinits=true]{biblatex}
\bibliography{biblio}
\renewcommand{\baselinestretch}{2}

@@

% Note that keywords are not normally used for peerreview paper.
\begin{IEEEkeywords}
acoustic scene classification, acoustic scene similarity retrieval, scattering transform, clustering, similarity measures.
\end{IEEEkeywords}

>>>>

\documentclass{IEEEtran}
%\usepackage{cite}
% *** GRAPHICS RELATED PACKAGES ***
%
\ifCLASSINFOpdf
  \usepackage[pdftex]{graphicx}
\fi
%
\usepackage[cmex10]{amsmath}

@@

\usepackage[backend=bibtex,style=numeric-comp,sorting=none,firstinits=true]{biblatex}
\bibliography{biblio}
%\renewcommand{\baselinestretch}{2}

@@

% Note that keywords are not normally used for peerreview paper.
\begin{IEEEkeywords}
unsupervised learning, classification algorithms, clustering algorithms, acoustic signal processing, wavelet transforms, audio databases, content-based retrieval, nearest neighbor searches, acoustic sensors, environmental sensors.
\end{IEEEkeywords}
